%-------------------------
% Resume in Latex
% Author : Francisca Almeida
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\input{glyphtounicode}

% Accent color matches falmeida.dev's theme (--primary, dark mode)
\definecolor{accent}{HTML}{A855F7}
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\bfseries\raggedright\large\color{accent}
}{}{0em}{}[\color{accent}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Francisca \textcolor{accent}{Almeida}} \\ \vspace{1pt}
    \small Lisbon, Portugal $|$ 
    \href{mailto:francisca04almeida@outlook.com}{\underline{francisca04almeida@outlook.com}} $|$ 
    \href{https://falmeida.dev}{\underline{falmeida.dev}} $|$
    \href{https://github.com/Francisca105}{\faGithub \hspace{1pt} \underline{francisca105}} $|$
    \href{https://www.linkedin.com/in/francisca-105-almeida/}{\faLinkedin \hspace{1pt} \underline{francisca-105-almeida}}
\end{center}

\small{Full-stack developer experienced in building scalable web applications and transitioning manual workflows into automated architectures. Strong foundation in backend systems, DevOps tooling, and technical leadership.}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Instituto Superior Técnico}{Lisbon, Portugal}
      {Master of Science in Computer Science and Engineering}{Sept. 2025 -- Present}
    \resumeSubheading
      {Instituto Superior Técnico}{Lisbon, Portugal}
      {Bachelor of Science in Computer Science and Engineering}{Sept. 2022 -- July 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Year Delegate} (2022 -- 2024): represented students in academic councils; re-elected in the 2nd year with the \textbf{highest number of votes} among all students at the college.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    % \resumeSubheading
    %   {Full-Stack Developer (Scholarship)}{June 2025 -- Present}
    %   {DSI Instituto Superior Técnico}{Lisbon, Portugal}
    %   \resumeItemListStart
    %     \resumeItem{Architected a digital system using a \textbf{Java and Spring Boot state machine} to automate academic course withdrawal processes for thousands of potential users.}
    %     \resumeItem{Modernized legacy manual workflows by collaborating with administrative staff to design \textbf{RESTful APIs} and integrate with existing internal university platforms.}
    %     \resumeItem{\textcolor{accent}{\textbf{Stack:}} Java, Spring Boot, SQL, REST APIs, System Architecture.}
    %   \resumeItemListEnd

    \resumeSubheading
      {Developer}{May 2026 -- Present}
      {ThinkOpen Solutions}{Lisbon, Portugal}
      \resumeItemListStart
        \resumeItem{Developer on the \textbf{Odoo migrations} team, focused primarily on testing with additional production support across the full migration lifecycle.}
        \resumeItem{Executed \textbf{go-lives}, pre-production environment setup, module upgrades, testing, and bug fixing for Odoo migration projects.}
        \resumeItem{Automating test planning, execution, and reporting workflows using \textbf{AI agents}.}
        \resumeItem{\textcolor{accent}{\textbf{Stack:}} Python, Odoo, PostgreSQL, XML.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Management Intern}{Aug. 2024 -- Nov. 2024}
      {Micro Harvest}{Lisbon, Portugal}
      \resumeItemListStart
        \resumeItem{Architected and deployed a centralized internal dashboard that slashed data processing latency for the operations team by automating Excel-based workflows.}
        \resumeItem{Developed custom data entry and report generation modules, significantly improving \textbf{scalability and usability} of internal data operations.}
        \resumeItem{\textcolor{accent}{\textbf{Stack:}} Next.js, FastAPI, Docker, SQL, Python.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXTRACURRICULAR ACTIVITIES-----------
\section{Extracurricular Activities}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{SINFO (Tech Conference)} $|$ \emph{Full-Stack Developer \& Team Leader}}{May 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Led the development team in maintaining the official web app for \textbf{1400+ users}; integrated \textbf{Grafana} dashboards for real-time attendee analytics.}
            \resumeItem{Led the complete architectural rebuild of the official SINFO website (\textbf{Next.js, TypeScript}), reaching \textbf{14.3k+ visits} during the event month and 6,000+ visits/month since; engineered a custom referral-tracking system integrated with Grafana for real-time marketing attribution.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Web.Dev (AeroTéc)} $|$ \emph{Web Developer \& Coordinator}}{Oct. 2023 -- Aug. 2025}
          \resumeItemListStart
            \resumeItem{Coordinated technical workshops and built internal recruitment/admin tools using \textbf{Express.js} and \textbf{MongoDB}.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{NEIIST (CS Student Org)} $|$ \emph{Web Developer \& Coordinator}}{Mar. 2024 -- Aug. 2025}
          \resumeItemListStart
            \resumeItem{Developed an end-to-end e-commerce merch sales page (\textbf{React/PostgreSQL}) that processed over \textbf{220 customer orders}.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------OPEN SOURCE CONTRIBUTIONS-----------
\section{Open Source}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Inbox Zero} $|$ \href{https://github.com/elie222/inbox-zero/pull/390}{\emph{Pull Request (Merged)}}}{May 2025}
          \resumeItemListStart
            \resumeItem{Improved UI consistency and addressed accessibility concerns in the task management interface.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, Python, Java, C/C++, SQL} \\
     \textbf{Frameworks}{: Next.js, React, Node.js, Express.js, Vue.js, FastAPI, Spring Boot, Tailwind CSS} \\
     \textbf{Tools \& Concepts}{: Docker, Git, Grafana, Figma, REST APIs, CI/CD, Agile (Scrum)} \\
     \textbf{Databases}{: MongoDB, MySQL, PostgreSQL, Firebase}
    }}
 \end{itemize}
%-------------------------------------------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Portuguese}{: Native} \\
     \textbf{English}{: Full Professional Proficiency (C1)} \\
     % \textbf{Spanish}{: Upper Intermediate (B2)} 
    }}
 \end{itemize}
 
\end{document}